---
title: "HW11"
author: "Hyeyeon Kim"
date: "5/3/2021"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = TRUE, message = FALSE)
library(tidyverse)
library(sp)
library(tmap)
library(tmaptools)
library(rgdal)
library(dplyr)
library(maptools)
library(gridExtra)
library(broom)
library(gpclib)
library(rgeos)
```

# Data Splitting

```{r ImportingData}
# Importing Shapefiles
Census_Geo <- readOGR("Census")

Real_Estate_Geo <- readOGR("Real_Estate")

#Importing normal .csv files
Real_Estate_csv <- read.csv("Real_Estate.csv")

Census <- read.csv("Census.csv")
```


```{r dataediting}
#selecting price, square feet, (and object ID for use in graphics)
re_data <- Real_Estate_csv %>% select(price = v_recentsales2_GIS_SALEPRICE, 
            sqft = v_recentsales2_GIS_SQFT, id = OBJECTID, 
            bedroom = v_recentsales2_BEDROOMS, year = v_recentsales2_YEARBUILT, 
            stories = v_recentsales2_STORIES, bathroom = v_recentsales2_BATHROOMS)


re_data <- re_data %>% mutate(stories = ceiling(stories))


re_data$bedroom <- ifelse(re_data$bedroom >= 4, yes = "More than 3", no = re_data$bedroom)

#Making variable for total number of bathrooms since the original variable was formatted differently
#Original variable was (number of full bath) . (number of half bath)
re_data <- re_data %>% mutate(half_bath = round(10*(bathroom %% 1), digits = 0), full_bath = floor(bathroom))


re_data <- re_data %>% mutate(bathroom = half_bath + full_bath)

re_data$full_bath_c <- ifelse(re_data$full_bath >= 4, yes = "More than 3", no = re_data$full_bath)
re_data$half_bath_c <- ifelse(re_data$half_bath >= 4, yes = "More than 3", no = re_data$half_bath)
re_data$bathroom_c <- ifelse(re_data$bathroom >= 4, yes = "More than 3", no = re_data$bathroom)


#Scrubbing price and sqft to not have commas or $ so that they're numeric
re_data <- re_data %>% 
  mutate(price = as.numeric(gsub(",", "", 
      as.character(sub("$", "", price , fixed=TRUE)))))
re_data <- re_data %>% mutate(sqft = as.numeric(gsub(",", "", sqft)), 
                              id = as.integer(id), 
         price = as.numeric(price), sqft = as.numeric(sqft))

#Adding in price/sqft variable
re_data <- re_data %>% mutate(ppsqft = price/sqft)


#Creating `own` variable based on ownership of property 
help <- Real_Estate_csv %>% select(bill = TaxParcel_PSTLCITY, zip = TaxParcel_ZIP5) %>%
  mutate(ny = "Rochester, NY") %>% mutate(site = paste(ny, zip))

ownership <- ifelse(help$bill == help$site, yes = TRUE, no = FALSE)


re_data <- re_data %>% mutate(own = ownership)

re_data <- re_data %>% mutate(pthou = price/1000)


set.seed(32)
samp <- sample(1:nrow(re_data),floor(.6*nrow(re_data)))

r_train_data_csv <- re_data[samp,] ## This is the 60% chunk
remain40 <- re_data[-samp,]  ## This is used for further bifurcation

samp2 <- sample(1:nrow(remain40),floor(.5*nrow(remain40)))

r_test_data_csv <- remain40[samp2,] ## First chunk of 20%
r_conf_data_csv <- remain40[-samp2,] ## Second Chunk of 20%

Reduce("intersect",list(r_train_data_csv,r_test_data_csv,r_conf_data_csv))


Census <- Census%>% select(poverty_level = F99x_poverty_level, 
          median_earnings = Median_earnings_in__past_12_mon, id = OBJECTID)

```

```{r realestate}
#Linking the shapefile to the normal .csv file
r_spdf_fortified <- tidy(Real_Estate_Geo, region = "OBJECTID")


r_spdf_fortified <- r_spdf_fortified %>% mutate(id = as.integer(id))

r_spdf_fortified1 <-  r_spdf_fortified %>%
  left_join(. , r_test_data_csv, by=c("id"="id"))

r_test_data <- na.omit(r_spdf_fortified1)

r_spdf_fortified2 <-  r_spdf_fortified %>%
  left_join(. , r_train_data_csv, by=c("id"="id"))

r_train_data <- na.omit(r_spdf_fortified2)

r_spdf_fortified3 <-  r_spdf_fortified %>%
  left_join(. , r_conf_data_csv, by=c("id"="id"))
r_conf_data <- na.omit(r_spdf_fortified3)

rm(help)
rm(r_spdf_fortified)
rm(re_data)
rm(Real_Estate_csv)
rm(Real_Estate_Geo)
rm(remain40)

```

```{r census}

#Linking the shapefile to normal .csv file
c_spdf_fortified <- tidy(Census_Geo, region = "OBJECTID")

Census <- Census %>% mutate(OBJECTID = as.integer(id))
c_spdf_fortified <- c_spdf_fortified %>% mutate(id = as.integer(id))

c_data <-  c_spdf_fortified %>%
  left_join(. , Census, by=c("id"="OBJECTID"))
rm(c_spdf_fortified)
rm(Census)

rm(Census_Geo)



```


```{r}
#save(r_train_data,file = "C:/Users/tcbra/OneDrive/Documents/emily/r_train_data.csv")
#save(r_test_data, file = "C:/Users/tcbra/OneDrive/Documents/emily/r_test_data.csv")
#save(r_conf_data, file = "C:/Users/tcbra/OneDrive/Documents/emily/r_conf_data.csv")
#save(c_data, file =  "C:/Users/tcbra/OneDrive/Documents/emily/c_data.csv")

#rm(r_train_data_csv)
#rm(r_test_data_csv)
#rm(r_conf_data_csv)
#rm(r_spdf_fortified1)
#rm(r_spdf_fortified2)
#rm(r_spdf_fortified3)

```




```{r}
c_data <- read.csv("c_data.csv")
r_train_data <- read.csv("r_train_data.csv")
```

# EDA

## Univariate Graphics

### Census

```{r plots}



c1 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group, fill = poverty_level), col = "black") +
  theme_void() +
  coord_map() +
  labs(title = "Poverty Level")

c2 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group, fill = median_earnings), col = "black") +
  theme_void() +
  coord_map() +
  labs(title = "Median Earnings")

c <- grid.arrange(c1, c2, ncol = 2)

```


### Real Estate

```{r, fig.height = 10}
r1 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = pthou, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Price in Thousands")


r2 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = sqft, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Square Footage")

r3 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = ppsqft, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Price per Square Footage")

r4 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = own, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Ownership")


r5 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = stories, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Number of Stories")


r6 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = bathroom_c, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Total Number of Bathrooms")


r7 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = half_bath_c, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Number of Half Bathrooms")

r8 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = full_bath_c, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Number of Full Bathrooms")

r9 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = bedroom, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Number of Bedrooms")

r10 <- ggplot() +
  geom_polygon(data = c_data, aes(x = long, y = lat, group = group), 
               col = "black", fill = "grey") + 
  geom_point(data = r_train_data, aes(col = year, x = long, y = lat, group = group), size = .25)+
  theme_void() +
  coord_map() +
  labs(title = "Year the House was Built")

r <- grid.arrange(r1, r2, r3, r4, r5, r6, r7, r8, r9, r10, ncol = 2)

```



```{r, fig.height = 10}

re1 <- ggplot(r_train_data, aes(pthou)) +
  geom_histogram() +
  labs(title = "Price in Thousands")

re2 <- ggplot(r_train_data, aes(sqft)) +
  geom_histogram()+
  labs(title = "Square Footage")

re3 <- ggplot(r_train_data, aes(ppsqft)) +
  geom_histogram()+
  labs(title = "Price per Square Footage")

t4 <- knitr::kable(table(r_train_data$stories), caption = "Number of Stories")

re4 <- ggplot(r_train_data, aes(stories)) + 
  geom_bar() +
  labs(title = "Number of Stories")

t5 <- knitr::kable(table(r_train_data$own), caption = "Ownership")

re5 <- ggplot(r_train_data, aes(own)) + 
  geom_bar() +
  labs(title = "Count of Ownership")

t6 <- knitr::kable(table(r_train_data$bathroom_c), caption = "Total Number of Bathrooms")

re6 <- ggplot(r_train_data, aes(bathroom)) +
  geom_bar()+
  labs(title = "Total Number of Bathrooms")

knitr::kable(table(r_train_data$half_bath_c), caption = "Number of Half Bathrooms")

re7 <- ggplot(r_train_data, aes(half_bath)) +
  geom_bar()+
  labs(title = "Number of Half Bathrooms")

knitr::kable(table(r_train_data$full_bath_c), caption = "Number of Full Bathrooms")

re8 <- ggplot(r_train_data, aes(full_bath)) +
  geom_bar()+
  labs(title = "Total Number of Full Bathrooms")

knitr::kable(table(r_train_data$bedroom), caption = "Number Bedrooms")

re10 <- ggplot(r_train_data, aes(year)) +
  geom_histogram()+
  labs(title = "Year Built")


t4
t5
t6

grid.arrange(re1, re2, re3, re4, re5, re6, re7, re8, re10, ncol = 2)


```


# Hypothesis Generation

```{r}
ggplot(data = r_train_data) +
  geom_boxplot(mapping = aes(x = sqft, y = bedroom, fill = bedroom)) +
  geom_boxplot(mapping = aes(x = sqft, y = bathroom_c, col = bathroom_c), alpha = .25) + 
  ylab("Count") +
  labs(title = "Square Footage as explained by Bedroom and Bathroom Quantity")

ggplot() +
  geom_polygon(data = c_data, aes(fill = median_earnings, x = long, y = lat, group = group), 
               col = "black") + 
  geom_point(data = r_train_data, aes(col = bedroom, x = long, y = lat, group = group, shape = own), size = 1, alpha = .25)+
  facet_grid(full_bath_c~half_bath_c) +
  coord_map() +
  ylab("Full Baths") +
  xlab("Half Baths") +
  labs(title = "Number of Bedrooms as explained by Numbers of Bathrooms")
```


## Hannah

```{r}
r_train_data$own_new <- as.integer(r_train_data$own)

# Relationship between the median earnings and poverty level
ggplot(data = c_data) +
  geom_point(mapping = aes(x = poverty_level, y = median_earnings)) +
  ylab("Median Earnings") +
  labs(title = "Relationship between Poverty Level and Median Earnings")

# Compare the ownership of the house by median earnings
ggplot() +
  geom_polygon(data = c_data, aes(fill = median_earnings, x = long, y = lat, group = group), 
               col = "black") + 
  geom_point(data = r_train_data, aes(col = own_new, x = long, y = lat, group = group, shape = own), size = 1, alpha = .25)+
  scale_color_gradient(low="white", high = "black") +
  theme_void() +
  coord_map() +
  labs(title = "Ownership of House Explained by Median Earnings")


# Compare the ownership of the house and stories of the house
ggplot(r_train_data) +
  geom_boxplot(aes(x = stories, y = own_new, group = own_new)) +
  ylab("Ownership") +
  xlab("Stories") +
  labs(title = "Number of Stories Explained by Ownership")

```


## Introduction

The testing data set has 1003 observations of 21 variables

\newpage

## Testing Data

```{r}
r_test_data <- read.csv("r_test_data.csv")
```

#### Section 4: Own vs. Stories

I was inspired by this graph here:

```{r}
r_test_data$own_new <- as.integer(r_test_data$own)

ggplot(r_test_data) +
  geom_bar(aes(x=own_new, group = stories)) +
  ylab("Stories") +
  xlab("Ownership") +
  labs(title = "Relatiosnhip between the number of stories and ownership")
```

Ownership = 0 means it is not owned by tenants and ownership = 1 means the house is owned.

I did linear regression between two variables, the number of stories and ownership of house.

```{r}
lm_4 <- lm(data=r_train_data, stories ~ own_new)
summary(lm_4)
```


### Observations

For the own vs. stories, we can conclude that there is no significant relationship between the number of stories and the ownership of the house even if the graph shows higher stories' houses are more owned by people. 
